Analysis of Programming Students' Prompts to Identify Interactions Patterns with Generative AI

### 2024-09-16 CSEDU2025/Paper.tex
classification

>>>>

% Spacing
We analyzed the time intervals between the user's interactions with the
CharlieBot. Our analysis showed that 12.93\% messages thar combatilized 40\% of
the conversations had response times longer than 60 minutes. In the case way,
1.29\% of the messages and 12.00\% of the conversations  containing messages
with delays exceeding 24 hours.

% Categories Time
